WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-05-16 Thesis.tex
v5.2.2 Intro

\acrfull{nwm} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Before using such multimodal data in a \acrshort{nwm}, it is necessary to transcode data into a format that can be ingested by the NWM. Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}. The resulting weather data also need to be accessed by many researchers and third-party applications such as logistic and agricultural insurance firms.
Existing weather data integration systems are based on monolithic or client-server architectures; hence, unable to benefit from novel computational models such as cloud computing and containers. Moreover, most of this software is proprietary or closed-source, making it difficult to customize them for an island like Sri Lanka with different weather seasons.
Therefore, in this research, we propose \acrfull{wdias} that utilizes modern architectural patterns such as microservices to achieve scalability, high availability, and low-cost operation based on cloud computing. The use of stateless microservices also enables \acrshort{wdias} to add new features on the fly with rollover capabilities. Moreover, \acrshort{wdias} provides a modular framework to integrate data from different sources, export into different formats, and add new functionality by adding extension modules.
We demonstrate the utility of \acrshort{wdias} using cloud-based experimental setup and weather-related synthetic workloads.

@@

\addcontentsline{toc}{chapter}{Dedication} 
\chapter*{Dedication}
I dedicate this thesis work to teachers, lectures, my family and specially colleagues at \acrfull{curw}. A special feeling of gratitude to my loving parents, Nandawathi Dissanayake and H.M.K. Karunarathne whose put countless sweats to support me throughout my entire life. My wife Jayani Kumarasinghe and my son Sasmitha Karunarathne who missed a lots of wonderful moments to give me freedom to work on my research.

>>>>

\acrfull{nwm} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Before using such multimodal data in a NWM, it is necessary to transcode data into a format that can be ingested by the \acrshort{nwm}. Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwm}. The resulting weather data also need to be accessed by many researchers and third-party applications such as logistic and agricultural insurance firms.
Existing weather data integration systems are based on monolithic or client-server architectures; hence, unable to benefit from novel computational models such as cloud computing and containerized applications. Moreover, most of these software are proprietary or closed-source, making it difficult to customize them for an island like Sri Lanka with different weather seasons.
Therefore, in this research, we propose \acrfull{wdias} that utilizes modern architectural patterns such as microservices to achieve scalability, high availability, and low-cost operation based on cloud computing. The use of stateless microservices also enables \acrshort{wdias} to add new features on the fly with rollover capabilities. Moreover, \acrshort{wdias} provides a modular framework to integrate data from different sources, export into different formats, and add new functionality by adding extension modules.
We demonstrate the utility of \acrshort{wdias} using cloud-based experimental setup and weather-related synthetic workloads.

@@

\addcontentsline{toc}{chapter}{Dedication} 
\chapter*{Dedication}
I dedicate this thesis work to teachers, lectures, my family and specially colleagues at \acrfull{curw}. A special feeling of gratitude to my loving parents, Nandawathi Dissanayake and H.M.K. Karunarathne whose put countless sweats to support me throughout my entire life. My wife Jayani Kumarasinghe and my son Sasmitha Karunarathne who missed a lots of wonderful moments to give me freedom to work on this research.

### 2020-05-16 introduction/sec_1-motivation.tex
v5.2.2 Intro

Weather data processed by one \acrshort{nwm} maybe used by several other NWSs, as well as by many third-party applications and researcher. For example, logistic companies could use the processed data with their models to plan and schedule their deliveries. Agricultural insurance companies can warn the farmers, as well as calculate premiums based on the anticipated weather patterns. Besides, farmers could rely on weather forecasts to plan their work. % decide what work to do on a given day. For example, drying hay is only possible in dry weather. Also, the aeronautical industry is particularly sensitive to weather conditions, precise weather forecasts are essential since before takeoff a flight need to check the conditions on expected route and at destination.
%required a provide platform to provide such 3rd party access, and use the data or process those based on their applications.

Data Integration and Analysis System (DIAS) \cite{Kawasaki2018DataReduction} and Meteorological Assimilation Data Ingest System (MADIS) \cite{Macdermaid2005ArchitectureP2.39} are two of the well-known Weather Data Integration and Assimilation (WDIA) systems. However, they are proprietary. Further, while \acrfull{fews} \cite{Werner2013TheSystem} is free to use, it is not open source. While a few other data integration systems exists, most of them are also proprietary or closed source. Thus, it is difficult and costly to customize such systems for an island like Sri Lanka which experience different kinds of weather seasons over the year \cite{NaveendrakumarFiveLanka}. % than that software originated need to be highly customized. Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors.
For example, \acrshort{fews} does not support FLO2D model integration, which is used by \acrshort{curw}'s workflows for water-level forecasting. %In such a case, it required to get support from the vendor to integrate and configure the system.

Existing WDIA systems are based on 
%Most of the software existing out there is not up to date with the latest technology concepts such as Cloud Computing. The modern architecture pattern such as microservice architecture was able to provide high scalability and availability, rather using 
the monolithic or client service architecture; hence, cannot benefit from technologies such as cloud computing to achieve high scalability and availability. Moreover, such systems cannot be updated or reconfigured without taking the system off line. Furthermore, they are platform specific. For example, while \acrshort{fews} can run on either Windows or Linux, downtime is needed to introduce any changes to the system. 
% Most existing systems required to shut down to update the system configuration such as \acrshort{fews}, but a system that is accessed by any third parties should be operating 99.9\% without any downtime and should allow adding new features on the fly with rollover capabilities. The proposed system should be independent of the platforms. But most software out there is platform dependent, as an example \acrshort{fews} can run on Windows and Linux. And should be independent underline infrastructure providers which gives much flexibility for the users to decide the best cost-effective way to host it.

>>>>

Weather data processed by a NWM maybe used by several other \acrshort{nwm}, as well as by many third-party applications and researcher. For example, logistic companies could use the processed data with their data models to plan and schedule their deliveries. Agricultural insurance companies can warn the farmers, as well as calculate premiums based on the anticipated weather patterns. Besides, farmers could rely on weather forecasts to plan their work.

Data Integration and Analysis System (DIAS) \cite{Kawasaki2018DataReduction} and Meteorological Assimilation Data Ingest System (MADIS) \cite{Macdermaid2005ArchitectureP2.39} are two of the well-known Weather Data Integration and Assimilation (WDIA) systems. However, those are proprietary systems. Further, while \acrfull{fews} \cite{Werner2013TheSystem} is free to use, but it is not open source. While a few other data integration systems exists, most of them are also proprietary or closed source. Thus, it is difficult and costly to customize such systems for an island like Sri Lanka which experience different kinds of weather seasons over the year \cite{NaveendrakumarFiveLanka}.
For example, \acrshort{fews} does not support FLO2D model integration, which is used by \acrshort{curw} to forecast water level.

Existing WDIA systems are based on the monolithic or client service architecture; hence, cannot benefit from technologies such as cloud computing to achieve high scalability and availability. Moreover, such systems cannot be updated or reconfigured without taking the system off line. Furthermore, these systems are platform specific. For example, while \acrshort{fews} can run on either Windows or Linux, downtime is needed to introduce any changes to the system.
